### 2017-12-07 manuscript.rmd

#Mantle canal SIMMAP Setup
#mantle_data = cdata[which(!is.na(cdata$Mantle.Canal)),]
#mantle = mantle_data$Mantle.Canal
#names(mantle)=rownames(mantle_data)
#MantleTree =  drop.tip(ultratree, which(!(ultratree$tip.label %in% names(mantle))))
#make.simmap(MantleTree, mantle, nsim = 100, message=FALSE) -> mantle_sim
```

```{r sex, echo=F, message=F, warning=F, include=F}
par(ask=F)

#These are commented out to avoid outputting the figure on every knit (remove comment to generate)

#Simmap SEX
plotTree(ultratree, lwd = 4)
colors = c("black", "red")
names(colors) = c("Dioecious", "Monoecious")
sex_sim %>% plotSimmap(lwd = 4, add = T, colors=colors)
nodelabels(pie=(describe.simmap(sex_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
 pdf("figures_raw/figure_5_raw_sex.pdf")
 densityMap(sex_sim)
 dev.off()
```

```{r palpons, echo=F, message=F, warning=F, include=F}
#Simmap PALPONS
 plotTree(ultratree, lwd = 4)
 colors = c("black", "red")
 names(colors) = c("Absent", "Present")
 palpons_sim %>% plotSimmap(lwd = 4, add = T,colors=colors)
 nodelabels(pie=(describe.simmap(palpons_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
 add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
 pdf("figures_raw/figure_5_raw_palpons.pdf")
 densityMap(palpons_sim)
 dev.off()
```

@@

#####Stochastic Character maps
```{r tentilla, echo=F, message=F,warning=F, fig.width=6.5, fig.height=7, fig.cap= "Stochastic character map of presence of tentilla"}
#Simmap TENTILLA
# plotTree(ultratree, lwd = 4)
# colors = c("black", "red")
# names(colors) = c("Absent", "Present")
# tentilla_sim %>% plotSimmap(lwd = 4, add = T,colors=colors)
# nodelabels(pie=(describe.simmap(tentilla_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
# add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(tentilla_sim)
```

```{r tentilla2, echo=F, message=F, warning=F, fig.width=6.5, fig.height=7, fig.cap= "Stochastic character map of presence of tentilla with *Physalia* included"}
#Simmap TENTILLA
# plotTree(ultratree, lwd = 4)
# colors = c("black", "red")
# names(colors) = c("Absent", "Present")
# tentilla_sim2 %>% plotSimmap(lwd = 4, add = T,colors=colors)
# nodelabels(pie=(describe.simmap(tentilla_sim2, plot=F)$ace) ,piecol=colors,cex=0.35)
# add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(tentilla_sim2)
```

```{r nectosome, echo=F, message=F, warning=F,  fig.width=6.5, fig.height=7, fig.cap= "Stochastic character map of presence of nectosome"}
#Simmap NECTOSOME
# plotTree(ultratree, lwd = 4)
# colors = c("black", "red")
# names(colors) = c("Absent", "Present")
# nectosome_sim %>% plotSimmap(lwd = 4, add = T,colors=colors)
# nodelabels(pie=(describe.simmap(nectosome_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
# add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(nectosome_sim)
```

```{r mantle, echo=F, message=F, warning=F,  fig.width=6.5, fig.height=7, fig.cap= "Stochastic character map of presence of nectosome"}
#Simmap NECTOSOME
# plotTree(ultratree, lwd = 4)
# colors = c("black", "red")
# names(colors) = c("Absent", "Present")
# nectosome_sim %>% plotSimmap(lwd = 4, add = T,colors=colors)
# nodelabels(pie=(describe.simmap(nectosome_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
# add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
#densityMap(mantle_sim)
```

```{r nectosome_pos, echo=F, message=F, warning=F,  fig.width=6.5, fig.height=7, fig.cap= "Stochastic character map for the evolution of the position of the nectosome. Cystonects were excluded as they do not have a nectosome."}
#SIMMAP NectoPos
# plotTree(ultratree, lwd = 4)
# colors = c("black", "red")
# names(colors) = c("Dorsal", "Ventral")
# necto_pos_sim %>% plotSimmap(lwd = 4, add = T)
# nodelabels(pie=(describe.simmap(necto_pos_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
# add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(necto_pos_sim)
```

>>>>

#Descending mantle Canal SIMMAP Setup
desc_mantle_data = cdata[which(!is.na(cdata$Desc.Mantle.Canal)),]
desc_mantle = desc_mantle_data$Desc.Mantle.Canal
names(desc_mantle)=rownames(desc_mantle_data)
DescMantleTree =  drop.tip(ultratree, which(!(ultratree$tip.label %in% names(desc_mantle))))
make.simmap(DescMantleTree, desc_mantle, nsim = 100, message=FALSE) -> desc_mantle_sim

#Ascending Mantle canal SIMMAP Setup
asc_mantle_data = cdata[which(!is.na(cdata$Asc.Mantle.Canal)),]
asc_mantle = asc_mantle_data$Asc.Mantle.Canal
names(asc_mantle)=rownames(asc_mantle_data)
AscMantleTree =  drop.tip(ultratree, which(!(ultratree$tip.label %in% names(asc_mantle))))
make.simmap(AscMantleTree, asc_mantle, nsim = 100, message=FALSE) -> asc_mantle_sim
```

```{r sex, echo=F, message=F, warning=F, include=F}
par(ask=F)
#Simmap SEX
plotTree(ultratree, lwd = 4)
colors = c("black", "red")
names(colors) = c("Dioecious", "Monoecious")
sex_sim %>% plotSimmap(lwd = 4, add = T, colors=colors)
nodelabels(pie=(describe.simmap(sex_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
sex_obj <- densityMap(sex_sim)
sex_obj$cols[1:length(sex_obj$cols)]<-colorRampPalette(colors=c("#4A4ACC", "orange"), space="Lab")(length(sex_obj$cols))
 pdf("figures_raw/figure_5_raw_sex.pdf")
 plot(sex_obj)
 dev.off()
```

```{r palpons, echo=F, message=F, warning=F, include=F}
#Simmap PALPONS
 plotTree(ultratree, lwd = 4)
 colors = c("black", "red")
 names(colors) = c("Absent", "Present")
 palpons_sim %>% plotSimmap(lwd = 4, add = T,colors=colors)
 nodelabels(pie=(describe.simmap(palpons_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
 add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
palpons_obj <- densityMap(palpons_sim)
palpons_obj$cols[1:length(palpons_obj$cols)]<-colorRampPalette(colors=c("#4A4ACC", "orange"), space="Lab")(length(palpons_obj$cols))
 pdf("figures_raw/figure_5_raw_palpons.pdf")
 plot(palpons_obj)
 dev.off()
```

@@

#####Stochastic Character maps
```{r tentilla, echo=F, message=F,warning=F, fig.width=6.5, fig.height=7, fig.cap= "Stochastic character map of presence of tentilla"}
#Simmap TENTILLA
# plotTree(ultratree, lwd = 4)
# colors = c("black", "red")
# names(colors) = c("Absent", "Present")
# tentilla_sim %>% plotSimmap(lwd = 4, add = T,colors=colors)
# nodelabels(pie=(describe.simmap(tentilla_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
# add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
tentilla_obj <- densityMap(tentilla_sim)
tentilla_obj$cols[1:length(tentilla_obj$cols)]<-colorRampPalette(colors=c("#4A4ACC", "orange"), space="Lab")(length(tentilla_obj$cols))
plot(tentilla_obj)
```

```{r tentilla2, echo=F, message=F, warning=F, fig.width=6.5, fig.height=7, fig.cap= "Stochastic character map of presence of tentilla with *Physalia* included"}
#Simmap TENTILLA
# plotTree(ultratree, lwd = 4)
# colors = c("black", "red")
# names(colors) = c("Absent", "Present")
# tentilla_sim2 %>% plotSimmap(lwd = 4, add = T,colors=colors)
# nodelabels(pie=(describe.simmap(tentilla_sim2, plot=F)$ace) ,piecol=colors,cex=0.35)
# add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
tentilla2_obj <- densityMap(tentilla_sim2)
tentilla2_obj$cols[1:length(tentilla2_obj$cols)]<-colorRampPalette(colors=c("#4A4ACC", "orange"), space="Lab")(length(tentilla2_obj$cols))
plot(tentilla2_obj)
```

```{r nectosome, echo=F, message=F, warning=F,  fig.width=6.5, fig.height=7, fig.cap= "Stochastic character map of presence of nectosome"}
#Simmap NECTOSOME
# plotTree(ultratree, lwd = 4)
# colors = c("black", "red")
# names(colors) = c("Absent", "Present")
# nectosome_sim %>% plotSimmap(lwd = 4, add = T,colors=colors)
# nodelabels(pie=(describe.simmap(nectosome_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
# add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
nectosome_obj <- densityMap(nectosome_sim)
nectosome_obj$cols[1:length(nectosome_obj$cols)]<-colorRampPalette(colors=c("#4A4ACC", "orange"), space="Lab")(length(nectosome_obj$cols))
plot(nectosome_obj)
```

```{r desc_mantle, echo=F, message=F, warning=F,  fig.width=6.5, fig.height=7, fig.cap= "Stochastic character map of presence of a descending mantle canal in the nectophores"}
#Simmap Descending Mantle Canal
# plotTree(ultratree, lwd = 4)
# colors = c("black", "red")
# names(colors) = c("Absent", "Present")
# desc_mantle_sim %>% plotSimmap(lwd = 4, add = T,colors=colors)
# nodelabels(pie=(describe.simmap(desc_mantle_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
# add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
desc_mantle_obj <- densityMap(desc_mantle_sim)
desc_mantle_obj$cols[1:length(desc_mantle_obj$cols)]<-colorRampPalette(colors=c("#4A4ACC", "orange"), space="Lab")(length(desc_mantle_obj$cols))
plot(desc_mantle_obj)
```

```{r asc_mantle, echo=F, message=F, warning=F,  fig.width=6.5, fig.height=7, fig.cap= "Stochastic character map of presence of an ascending mantle canal in the nectophores"}
#Simmap Ascending mantle canal
# plotTree(ultratree, lwd = 4)
# colors = c("black", "red")
# names(colors) = c("Absent", "Present")
# asc_mantle_sim %>% plotSimmap(lwd = 4, add = T,colors=colors)
# nodelabels(pie=(ascribe.simmap(asc_mantle_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
# add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
asc_mantle_obj <- densityMap(asc_mantle_sim)
asc_mantle_obj$cols[1:length(asc_mantle_obj$cols)]<-colorRampPalette(colors=c("#4A4ACC", "orange"), space="Lab")(length(asc_mantle_obj$cols))
plot(asc_mantle_obj)
```

```{r nectosome_pos, echo=F, message=F, warning=F,  fig.width=6.5, fig.height=7, fig.cap= "Stochastic character map for the evolution of the position of the nectosome. Cystonects were excluded as they do not have a nectosome."}
#SIMMAP NectoPos
# plotTree(ultratree, lwd = 4)
# colors = c("black", "red")
# names(colors) = c("Dorsal", "Ventral")
# necto_pos_sim %>% plotSimmap(lwd = 4, add = T)
# nodelabels(pie=(describe.simmap(necto_pos_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
# add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
necto_pos_obj <- densityMap(necto_pos_sim)
necto_pos_obj$cols[1:length(necto_pos_obj$cols)]<-colorRampPalette(colors=c("#4A4ACC", "orange"), space="Lab")(length(necto_pos_obj$cols))
plot(necto_pos_obj)
```
